TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-11-30 paper/paper.tex
Added more methods

\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
%\usepackage[hyperref=true, natbib=true, style=numeric, backend=bibtex]{biblatex}
\usepackage{graphicx}
%\bibliography{references.bib}

@@

@@

We propose to do a performance and behaviour analysis of different TCP
congestion control algorithms in a (simulated) datacenter network. Based on the
results, we will recommend datacenters on measures to keep providing a reliable
environment for customers when multiple congestion control algorithms are
active in the network, for example by using QoS or discouraging certain
congestion control algorithms.

@@

	\subsection{Comparing Performance}
	Two scenarios will be used to compare the performance of the TCP congestion algorithms:
	\begin{enumerate}
		\item The user owns one endpoint in the network. In this case only the sender side has a congestion algorithm applied.
		\item The user owns multiple endpoints in the network. In this case a congestion algorithm is applied at both the client and server side.
	\end{enumerate}

	The created environments are shown in figure \ref{fig:setup1} and figure \ref{fig:setup2}

	\begin{figure}[H] 
		\centering
			\caption{Test setup: Scenario 1}
  			\includegraphics[scale=0.5]{figs/setup1.png}
  		\label{fig:setup1}
	\end{figure}

	\begin{figure}[H] 
		\centering
			\caption{Test setup: Scenario 2}
			\includegraphics[scale=0.5]{figs/setup2.png}
  		\label{fig:setup2}
	\end{figure}

	In scenario 1 the server uses the same algorithm as the random node. The user node uses a different algorithm for the comparison. Tests in this scenario cover behavioral differences between TCP congestion algorithms when a user owns one node within a network. In scenario 2 the user server uses the same algorithm as the user node and the random server uses the same algorithm as the random node. Tests in this scenario cover behavioral differences between TCP congestion algorithms when a user owns two nodes within a network.

	In both scenarios the TCP congestion algorithms are tested for multiple characteristics:
	\begin{enumerate}
		\item TCP Window Size measured over time: 
		\item Bandwidth allocation: to determine whether using a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more bandwidth to a specific TCP connection.
		\item Round Trip Time: to determine the reason of the behaviour of a TCP congestion algorithm in combination with other TCP congestion algorithms.
	\end{enumerate}

	The tests conducted on the algorithms have different environment variables: packet loss and delay. Those environment variables are simulated using netem, which is a network emulation functionality in several Linux distributions. Packet loss and delay are chosen as the behavior of most TCP algorithms depend on those variables. The values for the environment variables per simulation run are shown in table ...

>>>>

\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[hyperref=true, natbib=true, style=numeric, backend=bibtex]{biblatex}
\usepackage{graphicx}
\bibliography{references.bib}

@@

% Copied from proposal
% Edited 27-11-2017

@@

This report includes a performance and behavior analysis of different TCP congestion control algorithms in a (simulated) multitenant datacenter network. Based on the results, we will recommend datacenters on measures to keep providing a reliable environment for customers when multiple congestion control algoritms are active in the network, for example using Quality of Service or discouraging certain congestion control algorithms. The main research question is: {\it How can a datacenter provide an reliable and performant environment for customers when multiple TCP congestion control algorithms are used in the
network?}

@@

	\subsection{Selecting TCP congestion algorithms}	
	In order to select the most common TCP congestion algorithms desk research will be performed. Results of scientific reports will show which algorithms are used more often than other algoritms. Based on those results a list of TCP congestion algorithms compatible with a multitenant datacenter environment will be composed.

	\subsection{Comparing Performance}
	One scenario will be used to compare the performance of the TCP congestion algorithms:
	\begin{enumerate}
		\item The user owns multiple endpoints in the network. In this case a congestion algorithm is applied at both the client and server side. This scenario applies to multitentant datacenter situations, where a user owns a server in the datacenter network and a node outside of the datacenter network.
	\end{enumerate}

	The created environment is shown in figure \ref{fig:setup1}.

	\begin{figure}[H] 
		\centering
  			\includegraphics[scale=0.5]{figs/setup2.png}
  			\caption{Test setup - Scenario 1}
  		\label{fig:setup1}
	\end{figure}

	In scenario 1 the user server uses the same algorithm as the user node and the random server uses the same algorithm as the random node. Tests in this scenario cover behavioral differences between TCP congestion algorithms when a user owns a node in the network of a multitenant datacenter.

	In both scenarios the TCP congestion algorithms are tested for multiple characteristics:
	\begin{enumerate}
		\item TCP Window Size measured over time: 
		\item Bandwidth allocation: to determine whether using a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more bandwidth to a specific TCP connection.
		\item Round Trip Time: to determine the reason of the behaviour of a TCP congestion algorithm in combination with other TCP congestion algorithms.
	\end{enumerate}
The tests conducted on the algorithms have different environment variables: packet loss and delay. Those environment variables are simulated using \texttt{netem}, which is a network emulation functionality in several Linux distributions. Packet loss and delay are chosen as the behavior of most TCP algorithms depend on those variables. The values for the environment variables per simulation run are shown in table ...		
\\
\\
	\begin{tabular}[H]{ | l | l | l |}
	\hline
	\textbf{Test} & \textbf{Delay} & \textbf{Packet loss} \\
	\hline 1 & 0ms & 0\%. \\
	\hline 2 & 0ms & 0.01\% \\
	\hline 3 & 0ms & 0.10\% \\
	\hline 4 & 0ms & 1.0\% \\
	\hline 1 & 0ms & 10\%. \\
	\hline
	\end{tabular}
